\titel

### 2014-03-10 presentation/presa.tex
Fix typo in presentation
Content of presentation
last changes

    \begin{itemize}
      \item From initial state to goal state?
      \item Create a planning plan.
      \item Assumptions:
        \begin{itemize}
          \item Determinism
          \item Full observability
          \item Reachability goals
        \end{itemize}
    \end{itemize}
  \end{columns}

@@

  \vspace{1cm}
  \uncover<3-> {What if picking up a block fails?}

@@

  Inspired by three new approaches in plan generation during that time:

  \begin{itemize}
    \item Planning graphs
    \begin{itemize}
      \item Nodes are actions and atomic facts arranged into alternate levels
      \item Edges from atomic facts to actions represents conditions
      \item Edges from actions to atomic facts represent true or false
    \end{itemize}
    \item Planning as a satisfiability method
    \item Heuristic search planning approach
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Forward state space search that combines hill-climbing and systematic search
    \item Heuristic estimating goal distances by ignoring delete lists - relaxed GRAPHPLAN
  \end{itemize}

@@

  Insert image on search state, enforced hill climbing, call relaxed Graphplan,
  inform search with goal distance estimate and maybe promising successors,
  solution plan or fail, possible search from scratch using hast table with
  visited states

\begin{frame}
  \frametitle{FF Planner (2001)}
    Same image

  To avoid wasting time in the presence of goal ordering:

  \begin{itemize}
    \item Goal deletion
    \item Goal agenda techniques
  \end{itemize}

@@

\begin{itemize}
\item  Perks
  \begin{itemize}
    \item No efficient algorithmic methods are possible for PSPACE-complete planning, inspired to focus on being efficient on a restricted subclass
    \item Most domains in the IPCC are simple in their structure and can be easily solves using greedy algorithms like FF
  \end{itemize}
\item Criticism
  \begin{itemize}
    \item Methods are motivated by observing example domains - might influence the completeness
    \item Pruning techniques are incomplete
    \item FF behaves poorly in domains with many dead-ends
    \item Solving these tasks with complete best-first search exhaust the memory for larger instances
  \end{itemize}
\end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Determinization
   \item Planning
	\begin{itemize}
	\item Partial state-action mapping using an initial empty hash-table
	\item Unexpected states are determinized and the synthesized plan (by FF) is put in the hash table
	\end{itemize}

\emph{ insert image how hash table is filled}

@@

  \begin{itemize}
    \item Shortcomings
	\begin{itemize}
        	\item Probabilistic effects are treated as equal

\includegraphics[scale=0.5]{images/blindfold.jpg}

	\end{itemize}
   \item Means of improvement
   \end{itemize}
\end{frame}

  \begin{itemize}
    \item Shortcomings
	\begin{itemize}
        	\item Probabilistic effects are treated as equal
	\item Only works well if the outcomes are likely
\includegraphics[scale=0.5]{images/direction-road-maze.jpg}
	\end{itemize}
   \item Means of improvement

@@

  \begin{itemize}
    \item Shortcomings
	\begin{itemize}
        	\item Probabilistic effects are treated as equal
	\item Only works well if the outcomes are likely
\includegraphics[scale=0.01]{images/direction-road-maze.jpg}
	\end{itemize}
   \item Means of improvement
	\begin{itemize}
	\item
	\end{itemize}
   \end{itemize}
\end{frame}

>>>>

    \begin{itemize}
      \item From initial state to goal state?
      \item Create a planning plan.
      \item Assumptions:
        \begin{itemize}
          \item Determinism
          \item Full observability
          \item Reachability goals
        \end{itemize}
    \end{itemize}

What if picking up a block fails?

  \end{columns}

@@

@@

  Inspired by new approaches in plan generation during that time:

  \begin{itemize}
    \item Planning graphs
    \begin{itemize}
      \item Nodes are actions and atomic facts arranged into alternate levels
      \item Edges from atomic facts to actions represents conditions
      \item Edges from actions to atomic facts represent true or false
    \end{itemize}
    \item Heuristic search planning approach
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Forward state space search 
    \item Heuristic relaxed GRAPHPLAN
  \end{itemize}

  \includegraphics{images/ffplan2.pdf}

@@

\begin{frame}
  \frametitle{FF Planner (2001)}
\begin{columns}

\column{0.4\textwidth}
  \includegraphics[width=0.8\textwidth]{images/ffplan.pdf}

\column{0.6\textwidth}
\begin{itemize}
	\item Expand the current state by doing a breadth-first search
	\item s:= the child of s for which the heuristic evaluates as closest to the solution
\end{itemize}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{FF Planner (2001)}
\begin{columns}

\column{0.4\textwidth}
  \includegraphics[width=0.8\textwidth]{images/ffplan.pdf}

\column{0.6\textwidth}
  To avoid wasting time in the presence of goal ordering:

  \begin{itemize}
    \item Goal deletion
    \item Goal agenda techniques
  \end{itemize}
\end{columns}
\end{frame}

@@

\begin{itemize}
\item  Perks
  \begin{itemize}
    \item Efficient on a restricted subclass
    \item simple IPCC domains can be easily solved using greedy algorithms like FF
  \end{itemize}
\item Criticism
  \begin{itemize}
    \item Methods are motivated by observing example domains
    \item Pruning techniques are incomplete
    \item FF behaves poorly in domains with many dead-ends
    \item Solving these tasks with complete best-first search exhaust the memory for larger instances
  \end{itemize}
\end{itemize}
\end{frame}

@@

  \begin{itemize}
    \item Determinization
    \item Planning
      \begin{itemize}
        \item Partial state-action mapping using an initial empty hash-table
        \item Unexpected states are determinized and the synthesized plan (by FF) is put in the hash table
      \end{itemize}
   \end{itemize}
\end{frame}

  \begin{itemize}
    \item Determinization
    \item Planning
 \includegraphics[width=\textwidth]{images/replan1.pdf}
   \end{itemize}
\end{frame}

  \begin{itemize}
    \item Determinization
    \item Planning
 \includegraphics[width=\textwidth]{images/replan2.pdf}
   \end{itemize}
\end{frame}

  \begin{itemize}
    \item Determinization
    \item Planning
 \includegraphics[width=\textwidth]{images/replan3.pdf}
   \end{itemize}
\end{frame}

  \begin{itemize}
    \item Determinization
    \item Planning
 \includegraphics[width=\textwidth]{images/replan4.pdf}
   \end{itemize}
\end{frame}

  \begin{itemize}
    \item Determinization
    \item Planning
 \includegraphics[width=\textwidth]{images/replan5.pdf}
   \end{itemize}
\end{frame}

  \begin{itemize}
    \item Shortcomings
      \begin{itemize}
        \item Probabilistic effects are treated as equal
          \includegraphics[scale=0.5]{images/blindfold.jpg}
      \end{itemize}
    \item Means of improvement
  \end{itemize}
\end{frame}

  \begin{itemize}
    \item Shortcomings
      \begin{itemize}
        \item Probabilistic effects are treated as equal
        \item Only works well if the outcomes are likely
          \includegraphics[scale=0.1]{images/direction-road-maze.jpg}
        \end{itemize}
    \item Means of improvement
  \end{itemize}
\end{frame}

  \begin{itemize}
    \item Shortcomings
      \begin{itemize}
        \item Probabilistic effects are treated as equal
        \item Only works well if the outcomes are likely
	\item Partial state-action policy does not guarantee quality
 %         \includegraphics[scale=0.01]{images/direction-road-maze.jpg}
      \end{itemize}
    \item Means of improvement
   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - Critism}
  \begin{itemize}
    \item Shortcomings
      \begin{itemize}
        \item Probabilistic effects are treated as equal
        \item Only works well if the outcomes are likely
	\item Partial state-action policy does not guarantee quality
	\item Picking Arbitrary grounded forms of the goal may end up being unreachable or a lot more expensive
%          \includegraphics[scale=0.01]{images/direction-road-maze.jpg}
      \end{itemize}
    \item Means of improvement
   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - Critism}
  \begin{itemize}
    \item Shortcomings
      \begin{itemize}
        \item Probabilistic effects are treated as equal
        \item Only works well if the outcomes are likely
	\item Partial state-action policy does not guarantee quality
	\item Picking Arbitrary grounded forms of the goal may end up being unreachable or a lot more expensive
 %         \includegraphics[scale=0.01]{images/direction-road-maze.jpg}
      \end{itemize}
    \item Means of improvement
      \begin{itemize}
        \item Addaptively repair the partial policy by for instance randomizing the determinization heuristics 
      \end{itemize}
   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - Critism}
  \begin{itemize}
    \item Shortcomings
      \begin{itemize}
        \item Probabilistic effects are treated as equal
        \item Only works well if the outcomes are likely
	\item Partial state-action policy does not guarantee quality
	\item Picking Arbitrary grounded forms of the goal may end up being unreachable or a lot more expensive
 %         \includegraphics[scale=0.01]{images/direction-road-maze.jpg}
      \end{itemize}
    \item Means of improvement
      \begin{itemize}
        \item Addaptively repair the partial policy by for instance randomizing the determinization heuristics 
	\item Sampling the grounded goals and testing with a relaxed reachability analysis
      \end{itemize}
   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - Critism}
  \begin{itemize}
    \item Shortcomings
      \begin{itemize}
        \item Probabilistic effects are treated as equal
        \item Only works well if the outcomes are likely
	\item Partial state-action policy does not guarantee quality
	\item Picking Arbitrary grounded forms of the goal may end up being unreachable or a lot more expensive
 %         \includegraphics[scale=0.01]{images/direction-road-maze.jpg}
      \end{itemize}
    \item Means of improvement
      \begin{itemize}
        \item Addaptively repair the partial policy by for instance randomizing the determinization heuristics 
	\item Sampling the grounded goals and testing with a relaxed reachability analysis
	\item Utilizing look ahead policies that simulate the actions
      \end{itemize}
   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - Questions}
  \begin{itemize}
    \item '' FF-Replan planner replans the same determinization of the problem when an unexpected state occurs. After replanning a new unexpected state might occur which makes the planner to replan again. Can the planner keep re- planning forever i.e. end up in deadlock? ''

@@

\begin{frame}
  \frametitle{FF-Replan - Questions}
  \begin{itemize}
    \item '' FF-Replan planner replans the same determinization of the problem when an unexpected state occurs. After replanning a new unexpected state might occur which makes the planner to replan again. Can the planner keep re- planning forever i.e. end up in deadlock? ''
   \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - Questions}

This is possible, but depends on the problem domain. 
\vspace{1cm}
\begin{columns}
\column{0.5\textwidth} Domain without cycles: no
\includegraphics[scale=0.4]{images/Question1a.png}

\column{0.5\textwidth} Domain with cycles: yes
\includegraphics[scale=0.4]{images/Question1b.png}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{FF-Replan - Questions}
  \begin{itemize}
	\item '' Since the planner replans the determinization each time an unexpected state occurs, is this algorithm suitable for real-time systems? ''

	\begin{itemize}
		\item Predictable domain: yes. \\
It is not as computationally intensive as using MDPs  and was the fastest planning algorithm within the competitors of the IPPC-06, making it very suitable.

	\end{itemize}

@@

\begin{frame}
  \frametitle{FF-Replan - Questions}
  \begin{itemize}
	\item '' Since the planner replans the determinization each time an unexpected state occurs, is this algorithm suitable for real-time systems? ''

	\begin{itemize}
		\item Unpredictable domain: probably not. \\
Unpredictable domains result in many unexpected states which cause for a significant amount of replanning.

Blocksworld:
\begin{itemize}
	\item Succes rate of 86\%
	\item Path of 73 actions
	\item Duration of 75s
\end{itemize}

\emph{Not recommended}, but still depends on the hardness of the real-time system.

	\end{itemize}
